Variation in Primary Care Prescribing in Wales due to COVID-19

### 2022-02-23 writing/paper.Rmd
Set predicitor variables to median/mode values for gls contrasts

```{r, gp-2020-percentiles, include=FALSE}
gp_2020_percentiles <- 
  data.frame(
    percentile = c(5, 25, 50, 75, 95),
    # wimd2019 = percentiles(gp_2020, wimd2019),
    ngp = percentiles(gp_2020, ngp),
    gp_load = percentiles(gp_2020, gp_load))
```

@@

```{r gls-month-fig, fig.cap="Dispensing by health board", eval=FALSE}
dd <- NULL
gls_month_fig <- list()
for(i in drugs){
  dd <- datadist(glsData(i))
  options(datadist = "dd")
  gls_month_fig[[i]] <- 
    Predict(best_bs_models[[i]], Month, 
            hboard = "BC", dispensing = FALSE, wimd2019 = "Med", ngp = 5, 
            gp_load = 1329.486, 
            PC1 = -0.1257104, PC2 = 0.1257104, PC3 = 0.1257104, PC4 = -0.09966945,
            conf.int = .95)

@@

```{r gls-hb-fig-panel, fig.cap="Dispensing by health board"}
dd <- NULL
gls_hb_fig <- list()
for(i in drugs_hb){
  dd <- datadist(glsData(i))
  options(datadist = "dd")
  gls_hb_fig[[i]] <- 
    Predict(best_bs_models[[i]], Month, hboard,
            dispensing = FALSE, wimd2019 = "Med", ngp = 5, 
            gp_load = 1329.486, 
            PC1 = -0.1257104, PC2 = 0.1257104, PC3 = 0.1257104, PC4 = -0.09966945,
            conf.int = .95)

@@

```{r, disp-contrast-fig, fig.cap="Dispensing status contrasts and 95% confidence limits from GLS models."}
disp_contrasts <- 
  list(
    all_drugs = contrast(best_bs_models$all_drugs, 
                         list(Month = 3:8, dispensing = TRUE),
                         list(Month = 3:8, dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    cortico = contrast(best_bs_models$cortico, 
                       list(Month = 3:8, dispensing = TRUE),
                       list(Month = 3:8, dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    paracet = contrast(best_bs_models$paracet, 
                       list(Month = 3:8, dispensing = TRUE),
                       list(Month = 3:8, dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    sal = contrast(best_bs_models$sal, 
                   list(Month = 3:8, dispensing = TRUE),
                   list(Month = 3:8, dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    vitd = contrast(best_bs_models$vitd, 
                    list(Month = 3:8, dispensing = TRUE),
                    list(Month = 3:8, dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame()
  ) %>% 
  bind_rows(.id = "drug")

@@

```{r, wimd-contrast-fig, fig.cap="WIMD contrasts and 95% confidence limits from GLS models."}
wimd_contrasts <- 
  list(
    cortico = contrast(best_bs_models$cortico, 
                       list(Month = 3:8, wimd2019 = "Low"),
                       list(Month = 3:8, wimd2019 = "High")) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    sal = contrast(best_bs_models$sal, 
                   list(Month = 3:8, wimd2019 = "Low"),
                   list(Month = 3:8, wimd2019 = "High")) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    ssri = contrast(best_bs_models$ssri, 
                       list(Month = 3:8, wimd2019 = "Low"),
                       list(Month = 3:8, wimd2019 = "High")) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    vitd = contrast(best_bs_models$vitd, 
                    list(Month = 3:8, wimd2019 = "Low"),
                    list(Month = 3:8, wimd2019 = "High")) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame()
  ) %>% 
  bind_rows(.id = "drug")

@@

```{r, ngp-contrast-fig, fig.cap="NGP contrasts and 95% confidence limits from GLS models."}
ngp_contrasts <- 
  list(
    oral_contra = contrast(best_bs_models$oral_contra, 
                       list(Month = 3:8, ngp = 3),
                       list(Month = 3:8, ngp = 8)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    sal = contrast(best_bs_models$sal, 
                   list(Month = 3:8, ngp = 3),
                   list(Month = 3:8, ngp = 8)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame()) %>% 
  bind_rows(.id = "drug")

@@

```{r, gpld-contrast-fig, fig.cap="NGP contrasts and 95% confidence limits from GLS models."}
gpld_contrasts <- 
  list(
    oral_contra = contrast(best_bs_models$oral_contra, 
                       list(Month = 3:8, gp_load = 1098),
                       list(Month = 3:8, gp_load = 1710)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame()) %>% 
  bind_rows(.id = "drug")

@@

contrasts %>% 
  ggplot(aes(x = Month, col = drug)) +
  geom_point(aes(y = Contrast), size = .5, position = position_dodge(.25)) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = position_dodge(.25),
                width = 0) +
  geom_hline(aes(yintercept = 0), colour = "grey") +
  ggthemes::theme_few() +
  theme(legend.spacing.y = unit(0.5, 'cm')) +
  guides(col = guide_legend(byrow = TRUE)) +
  labs(col = "Drug") +
  facet_wrap(~effect)

>>>>

```{r, gp-2020-percentiles, include=FALSE}
gp_2020_percentiles <- 
  data.frame(
    percentile = c(5, 25, 50, 75, 95),
    # wimd2019 = percentiles(gp_2020, wimd2019),
    ngp = percentiles(gp_2020, ngp),
    gp_load = percentiles(gp_2020, gp_load),
    PC1 = percentiles(gp_2020, PC1),
    PC2 = percentiles(gp_2020, PC2),
    PC3 = percentiles(gp_2020, PC3),
    PC4 = percentiles(gp_2020, PC4))

median(gp_2020$PC1)
```

@@

```{r gls-month-fig, fig.cap="Dispensing by health board", eval=FALSE}
dd <- NULL
gls_month_fig <- list()
for(i in drugs){
  dd <- datadist(glsData(i))
  options(datadist = "dd")
  gls_month_fig[[i]] <- 
    Predict(best_bs_models[[i]], Month, 
            hboard = "BC", dispensing = FALSE, wimd2019 = "Med", ngp = 5, 
            gp_load = 1329.486, 
            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
            conf.int = .95)

@@

```{r gls-hb-fig-panel, fig.cap="Dispensing by health board"}
dd <- NULL
gls_hb_fig <- list()
for(i in drugs_hb){
  dd <- datadist(glsData(i))
  options(datadist = "dd")
  gls_hb_fig[[i]] <- 
    Predict(best_bs_models[[i]], Month, hboard,
            dispensing = FALSE, wimd2019 = "Med", ngp = 5, 
            gp_load = 1329.486, 
            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
            conf.int = .95)

@@

```{r, disp-contrast-fig, fig.cap="Dispensing status contrasts and 95% confidence limits from GLS models."}
disp_contrasts <- 
  list(
    all_drugs = contrast(best_bs_models$all_drugs, 
                         list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
                              ngp = 5, gp_load = 1329,
                              PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                              PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                              dispensing = TRUE),
                         list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
                              ngp = 5, gp_load = 1329,
                              PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                              PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                              dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    cortico = contrast(best_bs_models$cortico, 
                       list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
                            ngp = 5, gp_load = 1329,
                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                            dispensing = TRUE),
                       list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
                            ngp = 5, gp_load = 1329,
                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                            dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    paracet = contrast(best_bs_models$paracet, 
                       list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
                            ngp = 5, gp_load = 1329,
                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                            dispensing = TRUE),
                       list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
                            ngp = 5, gp_load = 1329,
                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                            dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    sal = contrast(best_bs_models$sal, 
                   list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
                        ngp = 5, gp_load = 1329,
                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                        dispensing = TRUE),
                   list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
                        ngp = 5, gp_load = 1329,
                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                        dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    vitd = contrast(best_bs_models$vitd, 
                    list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
                         ngp = 5, gp_load = 1329,
                         PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                         PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                         dispensing = TRUE),
                    list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
                         ngp = 5, gp_load = 1329,
                         PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                         PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                         dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame()
  ) %>% 
  bind_rows(.id = "drug")

@@

```{r, wimd-contrast-fig, fig.cap="WIMD contrasts and 95% confidence limits from GLS models."}
wimd_contrasts <- 
  list(
    cortico = contrast(best_bs_models$cortico, 
                       list(Month = 3:8, hboard = "BC", wimd2019 = "Low", 
                            ngp = 5, gp_load = 1329,
                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                            dispensing = FALSE),
                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
                            ngp = 5, gp_load = 1329,
                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                            dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    sal = contrast(best_bs_models$sal, 
                   list(Month = 3:8, hboard = "BC", wimd2019 = "Low", 
                            ngp = 5, gp_load = 1329,
                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                            dispensing = FALSE),
                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
                            ngp = 5, gp_load = 1329,
                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                            dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    ssri = contrast(best_bs_models$ssri, 
                       list(Month = 3:8, hboard = "BC", wimd2019 = "Low", 
                            ngp = 5, gp_load = 1329,
                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                            dispensing = FALSE),
                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
                            ngp = 5, gp_load = 1329,
                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                            dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    vitd = contrast(best_bs_models$vitd, 
                    list(Month = 3:8, hboard = "BC", wimd2019 = "Low", 
                            ngp = 5, gp_load = 1329,
                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                            dispensing = FALSE),
                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
                            ngp = 5, gp_load = 1329,
                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                            dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame()
  ) %>% 
  bind_rows(.id = "drug")

@@

```{r, ngp-contrast-fig, fig.cap="NGP contrasts and 95% confidence limits from GLS models."}
ngp_contrasts <- 
  list(
    oral_contra = contrast(best_bs_models$oral_contra, 
                           list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
                                ngp = 3, gp_load = 1329,
                                PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                                PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                                dispensing = FALSE),
                           list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
                                ngp = 8, gp_load = 1329,
                                PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                                PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                                dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    sal = contrast(best_bs_models$sal, 
                   list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
                        ngp = 3, gp_load = 1329,
                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                        dispensing = FALSE),
                   list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
                        ngp = 8, gp_load = 1329,
                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                        dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame()) %>% 
  bind_rows(.id = "drug")

@@

```{r, gpld-contrast-fig, fig.cap="NGP contrasts and 95% confidence limits from GLS models."}
gpld_contrasts <- 
  list(
    oral_contra = contrast(best_bs_models$oral_contra, 
                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
                        ngp = 8, gp_load = 1098,
                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                        dispensing = FALSE),
                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
                        ngp = 8, gp_load = 1710,
                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                        dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame()) %>% 
  bind_rows(.id = "drug")

@@

contrasts %>% 
  ggplot(aes(x = Month, col = drug)) +
  geom_point(aes(y = Contrast), size = .5, position = position_dodge(.25)) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = position_dodge(.25),
                width = 0) +
  geom_hline(aes(yintercept = 0), colour = "grey") +
  ggthemes::theme_few() +
  theme(legend.spacing.y = unit(0.5, 'cm'),
        plot.caption = element_text(size = 8, hjust = 1)) +
  guides(col = guide_legend(byrow = TRUE)) +
  labs(col = "Drug") +
  facet_wrap(~effect) +
  labs(caption = paste0("Adjusted to Health Board = BC, Dispensing status = FALSE, WIMD = Med, Number GPs = 5, \nGP workload = 1329, PC1 = ", printnum(median(gp_2020$PC1))," PC2 = ", printnum(median(gp_2020$PC1)), " PC3 = ", printnum(median(gp_2020$PC3)), " PC4 = ", printnum(median(gp_2020$PC4))))
